Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review

### 2021-11-04 _bookdown_files/04-results.Rmd
Bookdown rendering
Inclusion of PRISMA checklist

The next part of our research question was to examine the way the syndemic conditions were studied in the literature. For the most often studied syndemic conditions, we found a high degree of variability in their measurement. Different authors used different scales or criteria and, even when the same scale or criteria was used, the cutoff or reference period differed among studies. For the sake of brevity, we will not provide a detailed description of the measurement method of the syndemic conditions studied in fewer than 10% of our sample. Detailed information about each of the papers included is presented in the supplementary material, part B ( \@ref(tab:DepressionTab) to \@ref(tab:AnxietyTab)).

@@

>>>>

The next part of our research question was to examine the way the syndemic conditions were studied in the literature. For the most often studied syndemic conditions, we found a high degree of variability in their measurement. Different authors used different scales or criteria and, even when the same scale or criteria was used, the cutoff or reference period differed among studies. For the sake of brevity, we will not provide a detailed description of the measurement method of the syndemic conditions studied in fewer than 10% of our sample. Detailed information about each of the papers included is presented in the supplementary material, part C ( \@ref(tab:DepressionTab) to \@ref(tab:AnxietyTab)).

@@

```{r framework_data, include=FALSE}
source("./scripts/create_framework_data.R", local = knitr::knit_global())
